---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trailcover

<!-- badges: start -->
<!-- badges: end -->

The goal of trailcover is to allow you to easily compare your tracks (gpx created by your physical walking, running, hiking, etc.) with official trails. 

## Installation

You can install the development version of trailcover from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("monkeywithacupcake/trailcover")
```

## Example

Package comes with example data:

 - Olympic National Park trails as geojson
 - Lake Angeles hiking track as gpx
 - Olympic National Forest trails as kmz
 
You can use the example data to see how to use the functions and then use your own

```{r example}
library(trailcover)

# read in the example track
# showing a hike from Lake Angeles in the Olympic National Park
this_track <- read_geo(trailcover_example("Lake_Angeles.gpx"))

# read in the example Olympic National Park trails
ex_onp_trails <- read_geo(trailcover_example("onp.geojson"))
# just focus on one trail for which we have a track
this_trail <- ex_onp_trails[ex_onp_trails$TRAIL_NAME == 'LAKE ANGELES TRAIL',]

# see the basic overlap map
map_track_v_trail(this_trail, this_track)

# see how much of the trail your track covers (distance)
onp_tracked <- get_coverage(big_sf = ex_onp_trails,
                            little_sf = this_track)

# get a map of the full trail network with your completions
map_coverage(trail_network = ex_onp_trails, covered_sf = onp_tracked)

# note that you do not have to do a full trail network
# this example shows the map only showing the two trails with
# coverage
map_coverage(trail_network = ex_onp_trails[ex_onp_trails$TRAIL_NAME %in%
                                             onp_tracked$TRAIL_NAME,],
             covered_sf = onp_tracked)

# and this shows just the one trail that we focused on
# note that the returned object is a plot, which can be
# modified
map_coverage(trail_network = this_trail,
             covered_sf = onp_tracked) +
  ggplot2::labs(title = "A new title")
# in this last case, you see that the trail is covered 72%
# the color of the track is based on the amount of coverage of that 
# trail and not of the whole system
```

