---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# trailcover

<!-- badges: start -->
<!-- badges: end -->

The goal of trailcover is to allow you to easily compare your tracks (gpx created by your physical walking, running, hiking, etc.) with official trails. 

## Installation

You can install the development version of trailcover from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("monkeywithacupcake/trailcover")
```

## Current State

transferring over functions from outside_oly - if you already mostly know how to use sf and r, feel free to try those functions.

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(trailcover)

# read in the example track
# showing a hike from Lake Angeles in the Olympic National Park
this_track <- read_geo(trailcover_example("Lake_Angeles.gpx"))

# read in the example Olympic National Park trails
ex_onp_trails <- read_geo(trailcover_example("onp.geojson"))
# just focus on one trail for which we have a track
this_trail <- ex_onp_trails[ex_onp_trails$TRAIL_NAME == 'LAKE ANGELES TRAIL',]

# see the basic overlap map
map_track_v_trail(this_trail, this_track)
```

